Eliminating Input-Based Attacks by Deriving Automated Encoders and Decoders from Context-free Grammars

### 2024-11-22 paper.tex
Fix spelling

All Software relies on input
devlo

It's the programming language job to prevent application developers from creating injection vulnerabilities.
Adding more sugger later will not make the cake any more tasty.

@@

Let's now tak a look at unparse_lang(k)
$lan = unparse_lang(k)$
$lan$ is always syntacticaly correct
$parse(lan) = k$ therefore there are no injections

>>>>

All Software relies on input

It's the programming language job to prevent application developers from creating injection vulnerabilities.
Adding more sugar later will not make the cake any more tasty.

@@

Let's now tak a look at unparse_lang(k)
$lan = unparse_lang(k)$
$lan$ is always syntactically correct
$parse(lan) = k$ therefore there are no injections
